---
title: "msAFP Load data"
output: html_notebook
date: "2024-06-28"
---

Goal: Import msAFP Cerner LIS and Maciel data

```{r}
library(tidyverse)
library(lubridate)
library(glue)
```

## Load Cerner
```{r}
col_spec <- cols(EMPI = col_character(),
                 HUP_MRN = col_character(),
                ORDER_ID = col_double(),
                ACCESSION = col_character(),
                ORDER_ALIAS_NUMBER = col_double(),
                TASK_ASSAY_CD = col_double(),
                DTA = col_character(),
                PERFORM_RESULT_ID = col_double(),
                RESULT_STATUS = col_character(),
                ASCII_TEXT = col_character(),
                RESULT_VALUE_NUMERIC = col_double(),
                RESULT_VALUE_ALPHA = col_character(),
                RESULT_VALUE_DT_TM = col_datetime(format = "%Y-%m-%d %H:%M:%S"),
                LESS_GREAT_FLAG = col_double(),
                EVENT_DT_TM = col_datetime(format = "%Y-%m-%d %H:%M:%S"),
                EVENT_TYPE_CD = col_integer(),
                PERFORM_DT_TM = col_datetime(format = "%Y-%m-%d %H:%M:%S"),
                RESULT_UPDT_DT_TM = col_datetime(format = "%Y-%m-%d %H:%M:%S"),
                SERVICE_RESOURCE = col_character(),
                DRAWN_DT_TM = col_datetime(format = "%Y-%m-%d %H:%M:%S"),
                RECEIVED_DT_TM = col_datetime() # Some are only day
              )

file_in <- "AFP_results.20240325b.csv"
file_dirs <- c("Pathology_Analytics", "msAFP")
if (.Platform$OS.type == 'windows') { fp_list <- c("I:", file_dirs, file_in)
} else { fp_list <- c("/Volumes", file_dirs, file_in) }
fp <- do.call(file.path, as.list(fp_list))

df <- read_csv(fp, col_types = col_spec)
```

```{r}
unlist(file_dirs)
```

## Process Cerner
### Fix inputs
```{r}
# Fix time zone
df <- df %>%
  mutate(across(ends_with("DT_TM"), ~ . - hours(4)))
```

```{r}
# Extract accession last 9
df <- df %>%
  mutate(ACCESSION_NUM = paste(substring(ACCESSION, 9, 12), 
                               substring(ACCESSION, 14, 19),
                               sep="") %>% as.numeric())
```

```{r}
# Fix MRN
df <- df %>%
  mutate(HUP_MRN = sprintf("%09d", as.numeric(HUP_MRN)))
```

```{r}
# Set result status as ordered factor
df <- df %>%
  mutate(RESULT_STATUS = factor(x=RESULT_STATUS, levels = c("Corrected", "Verified", "Old Corrected", "Old Verified", "Old Performed"), 
                                ordered=TRUE))
```

```{r}
# Pick final result
## TODO -- pick latest EMPI
pre_df_sum <- df %>%
  summarize(N=n(),
            N_pts = n_distinct(EMPI),
            N_orders = n_distinct(ORDER_ID),
            N_results = n_distinct(ORDER_ID, TASK_ASSAY_CD))

df <- df %>%
  group_by(ORDER_ID, TASK_ASSAY_CD) %>%
    arrange(desc(EVENT_DT_TM)) %>%
    slice(1) %>%
    ungroup()

log_text <- 'Pick final result'
glue('[FILTER] {text}: Rows {n_start}->{n_end} (Diff: {n_diff})',
      text=log_text, n_start = pre_df_sum$N, n_end = nrow(df), n_diff = n_start - n_end)
glue('[FILTER] {text}: Patients {pt_start}->{pt_end} (Diff: {pt_diff})',
      text=log_text, pt_start = pre_df_sum$N_pts, pt_end = n_distinct(df$EMPI), pt_diff = pt_start - pt_end)
glue('[FILTER] {text}: Results {result_start}->{result_end} (Diff: {result_diff})',
        text=log_text, result_start = pre_df_sum$N_results, result_end = n_distinct(df$ORDER_ID, df$TASK_ASSAY_CD), result_diff = result_start - result_end)

df %>% count(RESULT_STATUS)
```

TODO: What patients am I dropping with picking final result?

## Pivot Cerner
```{r}
orders <- df %>%
              select(EMPI, ACCESSION_NUM, ORDER_ID, DRAWN_DT_TM) %>%
                distinct()

df_wide_1 <- df %>%
  select(ORDER_ID, DTA, ASCII_TEXT) %>%
  filter(!DTA %in% c("AFP", "AFPI", "Est'd Date of Delivery")) %>%
  filter(!is.na(ASCII_TEXT)) %>%
  pivot_wider(id_cols = ORDER_ID, names_from = DTA, values_from = ASCII_TEXT) %>%
  mutate(weight = as.numeric(`Maternal Weight.`))

df_wide_2 <- df %>% 
  select(ORDER_ID, DTA, RESULT_VALUE_NUMERIC) %>%
  filter(DTA == "AFP") %>%
  filter(!is.na(RESULT_VALUE_NUMERIC)) %>%
  pivot_wider(id_cols = ORDER_ID, names_from = DTA, values_from = RESULT_VALUE_NUMERIC)

df_wide_3 <- df %>%
  select(ORDER_ID, DTA, RESULT_VALUE_DT_TM) %>%
  filter(DTA == "Est'd Date of Delivery") %>%
  filter(!is.na(RESULT_VALUE_DT_TM)) %>%
  pivot_wider(id_cols = ORDER_ID, names_from = DTA, values_from = RESULT_VALUE_DT_TM)

df_wide_4 <- df %>%
  select(ORDER_ID, DTA, RESULT_VALUE_ALPHA) %>%
  filter(DTA == "AFPI") %>%
  filter(!is.na(RESULT_VALUE_ALPHA)) %>%
  pivot_wider(id_cols = ORDER_ID, names_from = DTA, values_from = RESULT_VALUE_ALPHA)

df_wide <- orders %>%
              full_join(df_wide_1, by="ORDER_ID") %>%
              full_join(df_wide_2, by="ORDER_ID") %>%
              full_join(df_wide_3, by="ORDER_ID") %>%
              full_join(df_wide_4, by="ORDER_ID")
```
## Create dataset
### Filters
#### Exclude for EDD missingness
```{r}
# of Rows before Filtering
pre_df_sum <- df_wide %>%
  summarize(N=n(),
            N_pts = n_distinct(EMPI),
            N_orders = n_distinct(ORDER_ID),
            N_pt_days = n_distinct(EMPI, DRAWN_DT_TM))

df_wide <- df_wide %>%
  filter(!is.na(`Est'd Date of Delivery`))

log_text <- 'EDD missing'
glue('[FILTER] {text}: Rows {n_start}->{n_end} (Diff: {n_diff})',
      text=log_text, n_start = pre_df_sum$N, n_end = nrow(df_wide), n_diff = n_start - n_end)
glue('[FILTER] {text}: Patients {pt_start}->{pt_end} (Diff: {pt_diff})',
      text=log_text, pt_start = pre_df_sum$N_pts, pt_end = n_distinct(df_wide$EMPI), pt_diff = pt_start - pt_end)
glue('[FILTER] {text}: Pts-days {pt_days_start}->{pt_days_end} (Diff: {pt_days_diff})',
        text=log_text, pt_days_start = pre_df_sum$N_pt_days, pt_days_end = n_distinct(df_wide$EMPI, df_wide$DRAWN_DT_TM), pt_days_diff = pt_days_start - pt_days_end)
```

#### Add Gestational Age 
```{r}
df_wide <- df_wide %>%
  mutate(days_until_EDD = difftime(`Est'd Date of Delivery`, as_date(DRAWN_DT_TM), units="days") %>% as.numeric,
         gestational_age_days = 40 * 7 - days_until_EDD,
         gestational_age_weeks = gestational_age_days / 7,
         gestational_age = paste(floor(gestational_age_weeks), gestational_age_days %% 7, sep="+"))
```

#### Exclude GA >= 22 or GA < 15
```{r}
pre_df_sum <- df_wide %>%
  summarize(N=n(),
            N_pts = n_distinct(EMPI),
            N_orders = n_distinct(ORDER_ID),
            N_pt_days = n_distinct(EMPI, DRAWN_DT_TM))

df_wide <- df_wide %>%
              filter(gestational_age_weeks >= 15 &
                       gestational_age_weeks < 22)
log_text <- 'GA <15 or >= 22'
glue('[FILTER] {text}: Rows {n_start}->{n_end} (Diff: {n_diff})',
      text=log_text, n_start = pre_df_sum$N, n_end = nrow(df_wide), n_diff = n_start - n_end)
glue('[FILTER] {text}: Patients {pt_start}->{pt_end} (Diff: {pt_diff})',
      text=log_text, pt_start = pre_df_sum$N_pts, pt_end = n_distinct(df_wide$EMPI), pt_diff = pt_start - pt_end)
glue('[FILTER] {text}: Pts-days {pt_days_start}->{pt_days_end} (Diff: {pt_days_diff})',
        text=log_text, pt_days_start = pre_df_sum$N_pt_days, pt_days_end = n_distinct(df_wide$EMPI, df_wide$DRAWN_DT_TM), pt_days_diff = pt_days_start - pt_days_end)
```

#### Exclude for missing AFP result
```{r}
pre_df_sum <- df_wide %>%
  summarize(N=n(),
            N_pts = n_distinct(EMPI),
            N_orders = n_distinct(ORDER_ID),
            N_pt_days = n_distinct(EMPI, DRAWN_DT_TM))

df_wide <- df_wide %>%
  filter(!is.na(AFP))

log_text <- 'AFP missing'
glue('[FILTER] {text}: Rows {n_start}->{n_end} (Diff: {n_diff})',
      text=log_text, n_start = pre_df_sum$N, n_end = nrow(df_wide), n_diff = n_start - n_end)
glue('[FILTER] {text}: Patients {pt_start}->{pt_end} (Diff: {pt_diff})',
      text=log_text, pt_start = pre_df_sum$N_pts, pt_end = n_distinct(df_wide$EMPI), pt_diff = pt_start - pt_end)
glue('[FILTER] {text}: Pts-days {pt_days_start}->{pt_days_end} (Diff: {pt_days_diff})',
        text=log_text, pt_days_start = pre_df_sum$N_pt_days, pt_days_end = n_distinct(df_wide$EMPI, df_wide$DRAWN_DT_TM), pt_days_diff = pt_days_start - pt_days_end)
```

#### Exclude for missing weight
```{r}
pre_df_sum <- df_wide %>%
  summarize(N=n(),
            N_pts = n_distinct(EMPI),
            N_orders = n_distinct(ORDER_ID),
            N_pt_days = n_distinct(EMPI, DRAWN_DT_TM))

df_wide <- df_wide %>%
  filter(!is.na(weight))

log_text <- 'Weight missing'
glue('[FILTER] {text}: Rows {n_start}->{n_end} (Diff: {n_diff})',
      text=log_text, n_start = pre_df_sum$N, n_end = nrow(df_wide), n_diff = n_start - n_end)
glue('[FILTER] {text}: Patients {pt_start}->{pt_end} (Diff: {pt_diff})',
      text=log_text, pt_start = pre_df_sum$N_pts, pt_end = n_distinct(df_wide$EMPI), pt_diff = pt_start - pt_end)
glue('[FILTER] {text}: Pts-days {pt_days_start}->{pt_days_end} (Diff: {pt_days_diff})',
        text=log_text, pt_days_start = pre_df_sum$N_pt_days, pt_days_end = n_distinct(df_wide$EMPI, df_wide$DRAWN_DT_TM), pt_days_diff = pt_days_start - pt_days_end)
```

#### Check for further missingeness
```{r}
InputData <- c("Indication for testing", "EDD Determ by", "Number of Fetuses.", 
                          "weight", "Insulin Depend. Diabetic", "Maternal Race.", 
                          "Hx of Neural Tube Defects", "AFP", "Est'd Date of Delivery")
df_wide %>%
  summarise(across(all_of(InputData), ~ sum(is.na(.))))
```

#### Exclude repeats within pregnancy
##### Check samples flagged as repeat testing
```{r}
tmp <- df_wide %>%
  filter(`Indication for testing` == 'Repeat testing') %>%
  select(EMPI, ORDER_ID) %>%
  mutate(flagged_as_repeat = TRUE)

n_repeats <- df_wide %>%
  inner_join(tmp %>% select(EMPI) %>% distinct(), by=c("EMPI")) %>%
  left_join(tmp, by=c("EMPI", "ORDER_ID")) %>%
  mutate(flagged_as_repeat=if_else(is.na(flagged_as_repeat), FALSE, flagged_as_repeat)) %>% 
  group_by(EMPI) %>%
    mutate(weeks_difference = difftime(DRAWN_DT_TM, DRAWN_DT_TM[flagged_as_repeat], units='weeks') %>% as.numeric()) %>%
    filter((n() > 1) & 
              any(abs(weeks_difference) < 20 & 
                    (weeks_difference != 0)) 
           ) %>%
    ungroup() %>%
  select(EMPI, ORDER_ID, `Indication for testing`, flagged_as_repeat, DRAWN_DT_TM, weeks_difference)

glue('Cases flagged as repeats that appear to warrange exclusion: {nrow(n_repeats)}')
```


##### Identify repeat testing
```{r}
EMPI_repeats <- df_wide %>%
  count(EMPI) %>%
  filter(n > 1)
EMPI_repeats

# Identify EMPIs with tests within 20 weeks
cases_to_exclude <- df_wide %>%
  inner_join(EMPI_repeats %>% select(EMPI) %>% distinct(), by=c("EMPI")) %>%
  arrange(EMPI, DRAWN_DT_TM) %>%
  group_by(EMPI) %>%
    mutate(weeks_difference = difftime(DRAWN_DT_TM, lag(DRAWN_DT_TM), units='weeks') %>% as.numeric()) %>%
    filter(!is.na(weeks_difference) & 
                  weeks_difference < 20) %>%
    ungroup() %>%
  select(EMPI, ORDER_ID, `Indication for testing`, DRAWN_DT_TM, weeks_difference)

df_wide %>%
  inner_join(cases_to_exclude %>% select(EMPI) %>% distinct(), by=c("EMPI")) %>%
  left_join(cases_to_exclude %>% select(EMPI, ORDER_ID, weeks_difference), by=c("EMPI", "ORDER_ID")) %>%
  select(EMPI, ORDER_ID, `Indication for testing`, DRAWN_DT_TM, weeks_difference, gestational_age_weeks, AFP) %>%
  arrange(EMPI, DRAWN_DT_TM)
```

##### Apply repeat testing exclusion
```{r}
pre_df_sum <- df_wide %>%
  summarize(N=n(),
            N_pts = n_distinct(EMPI),
            N_orders = n_distinct(ORDER_ID),
            N_pt_days = n_distinct(EMPI, DRAWN_DT_TM))

df_wide <- df_wide %>%
  anti_join(cases_to_exclude, by=c("EMPI", "ORDER_ID"))

log_text <- 'Duplicate testing within pregnancy'
glue('[FILTER] {text}: Rows {n_start}->{n_end} (Diff: {n_diff})',
      text=log_text, n_start = pre_df_sum$N, n_end = nrow(df_wide), n_diff = n_start - n_end)
glue('[FILTER] {text}: Patients {pt_start}->{pt_end} (Diff: {pt_diff})',
      text=log_text, pt_start = pre_df_sum$N_pts, pt_end = n_distinct(df_wide$EMPI), pt_diff = pt_start - pt_end)
glue('[FILTER] {text}: Pts-days {pt_days_start}->{pt_days_end} (Diff: {pt_days_diff})',
        text=log_text, pt_days_start = pre_df_sum$N_pt_days, pt_days_end = n_distinct(df_wide$EMPI, df_wide$DRAWN_DT_TM), pt_days_diff = pt_days_start - pt_days_end)
```

### Adjust variables
#### Race
##### Describe Race variable
```{r}
df_wide %>% count(`Maternal Race.`)
```

##### Remap race
```{r}
df_wide <- df_wide %>%
  mutate(race = case_when(
                    `Maternal Race.` %in% c("White", "White3") ~ 'White',
                    `Maternal Race.` %in% c("Asia", "Asian") ~ 'Asian',
                    `Maternal Race.` %in% c("Unknown", "Other") ~ 'Other',
                    TRUE ~ `Maternal Race.`),
         race_factor = factor(race, levels = c("White", "Black", "Hispanic", "Asian", "Other")),
         raceBlack = if_else(race_factor == "Black", 1, 0)
      )

df_wide %>%
  count(race_factor, raceBlack)
```
## Load Maciel
```{r}
maciel_col_spec <- cols(
  ACCESSION = col_double(),
  USER_ID = col_character(),
  PAT_DOB = col_character(),
  NAME_LAST = col_character(),
  NAME_FIRST = col_character(),
  NAME = col_character(),
  TEST_TYPE = col_character(),
  GRAV = col_double(),
  PARA = col_double(),
  ABORT = col_double(),
  SAB = col_double(),
  PAT_HT_FT = col_double(),
  PAT_HT_IN = col_double(),
  PAT_WT = col_double(),
  PAT_RACE = col_character(),
  PHYS_CODE = col_double(),
  ATTENTION1 = col_character(),
  PHYS_CODE2 = col_logical(),
  ATTENTION2 = col_logical(),
  DIABETIC = col_character(),
  SMOKE = col_character(),
  CIG_DAY = col_double(),
  YRS_EDUC = col_double(),
  PHYS_ACT = col_logical(),
  VAG_BLOOD = col_logical(),
  WEEK_BLEED = col_logical(),
  NTD_HIST = col_character(),
  NTD_DESC = col_logical(),
  ILL_AC_CR = col_logical(),
  ILL_CODE1 = col_logical(),
  ILL_CODE2 = col_logical(),
  MULT_FETUS = col_double(),
  WT_CLDLB = col_double(),
  WT_CLDOZ = col_double(),
  AGE_CLD_YR = col_double(),
  AGE_CLD_MN = col_double(),
  DATE_LMP = col_character(),
  DATE_US = col_character(),
  GAGE_US = col_double(),
  DATE_PE = col_character(),
  GAGE_PE = col_logical(),
  RPT_GMETH = col_character(),
  DO_FDS = col_character(),
  RPT_DATE = col_character(),
  TO_WHOM = col_double(),
  TO_WHOM2 = col_logical(),
  DOWN_CODE = col_character(),
  NTD_CODE = col_character(),
  AF_CODE = col_logical(),
  HCG_CODE = col_character(),
  NEW_DOWN = col_logical(),
  NEW_NTD = col_character(),
  NEW_AF = col_logical(),
  NEW_HCG = col_logical(),
  FU_CODE = col_logical(),
  FU_DOB = col_logical(),
  FU_WT_LB = col_double(),
  FU_WT_OZ = col_double(),
  FU_COMMENT = col_logical(),
  MS1_NUM = col_double(),
  MS1_DRAWN = col_character(),
  MS1_RECVD = col_character(),
  MS1_TESTED = col_character(),
  MS1_RESULT = col_double(),
  MS1_MOM = col_double(),
  MS1_RISK = col_double(),
  MS1_GEST = col_double(),
  MS1_MATAGE = col_double(),
  HCG1 = col_double(),
  HCG1_MOM = col_double(),
  EST1 = col_double(),
  EST1_MOM = col_double(),
  INHA1 = col_double(),
  INHA1_MOM = col_double(),
  ONTD1_RISK = col_double(),
  ONTD1_FLAG = col_character(),
  T181_RISK = col_double(),
  ASFIRST1 = col_character(),
  SLOS1RISK = col_double(),
  U_RISK1 = col_logical(),
  MS1_STATUS = col_character(),
  MS2_NUM = col_double(),
  MS2_DRAWN = col_character(),
  MS2_RECVD = col_character(),
  MS2_TESTED = col_character(),
  MS2_RESULT = col_double(),
  MS2_MOM = col_double(),
  MS2_RISK = col_double(),
  MS2_GEST = col_double(),
  MS2_MATAGE = col_double(),
  HCG2 = col_double(),
  HCG2_MOM = col_double(),
  EST2 = col_double(),
  EST2_MOM = col_double(),
  INHA2 = col_double(),
  INHA2_MOM = col_double(),
  ONTD2_RISK = col_double(),
  ONTD2_FLAG = col_logical(),
  T182_RISK = col_double(),
  ASFIRST2 = col_character(),
  SLOS2RISK = col_double(),
  U_RISK2 = col_logical(),
  MS2_STATUS = col_character(),
  MS3_NUM = col_double(),
  MS3_DRAWN = col_character(),
  MS3_RECVD = col_character(),
  MS3_TESTED = col_character(),
  MS3_RESULT = col_double(),
  MS3_MOM = col_double(),
  MS3_RISK = col_double(),
  MS3_GEST = col_double(),
  MS3_MATAGE = col_double(),
  HCG3 = col_double(),
  HCG3_MOM = col_double(),
  EST3 = col_double(),
  EST3_MOM = col_double(),
  INHA3 = col_double(),
  INHA3_MOM = col_double(),
  ONTD3_RISK = col_double(),
  ONTD3_FLAG = col_logical(),
  T183_RISK = col_double(),
  ASFIRST3 = col_character(),
  SLOS3RISK = col_double(),
  U_RISK3 = col_logical(),
  MS3_STATUS = col_character(),
  AF1_PEND = col_double(),
  AF1_NUM = col_logical(),
  AF1_DRAWN = col_logical(),
  AF1_RECVD = col_logical(),
  AF1_TESTED = col_logical(),
  AF1_RESULT = col_double(),
  AF1_SD = col_double(),
  AF1_GEST = col_double(),
  AF1_MATAGE = col_double(),
  AF1_RISK = col_logical(),
  ACHE = col_logical(),
  ACHE_PCHE = col_double(),
  CONTAM_MAT = col_logical(),
  CONTAM_FET = col_logical(),
  DATA_ENTRY = col_character(),
  LAST_ENTRY = col_character(),
  AF1_STATUS = col_logical()
)
  
file_in <- "MPI_02Feb2024_1513.csv"
file_dirs <- c("Pathology_Analytics", "msAFP")
if (.Platform$OS.type == 'windows') { fp_list <- c("I:", file_dirs, file_in)
} else { fp_list <- c("/Volumes", file_dirs, file_in) }
fp <- do.call(file.path, as.list(fp_list))

maciel_df <- read_csv(fp, col_types = maciel_col_spec)
```

### Process Maciel
```{r}
# Handle date
maciel_df <- maciel_df %>%
  mutate(test_dt_tm = parse_date_time(MS1_TESTED, order="%-m/%-d/%Y %-H:%M:%S"))
```

#### Clean
```{r}
# Handle GA
maciel_df <- maciel_df %>%
  filter(MS1_GEST >= 15 &
                       MS1_GEST < 22)
```

### Merge into Cerner dataset
```{r}
### Merge
df_wide <- df_wide %>%
  left_join(maciel_df %>%
              select(starts_with('MS1')), by=c("ACCESSION_NUM"="MS1_NUM"), suffix=c("", ".maciel"))
```

### Check
```{r}
discordant_AFPs <- df_wide %>%
  filter(!is.na(MS1_RESULT)) %>%
  filter(MS1_RESULT != AFP) %>%
  select(EMPI, ORDER_ID, AFP, MS1_RESULT)
discordant_AFPs
```

### Exclude orders with discordant AFPs
```{r}
pre_df_sum <- df_wide %>%
  summarize(N=n(),
            N_pts = n_distinct(EMPI),
            N_orders = n_distinct(ORDER_ID),
            N_pt_days = n_distinct(EMPI, DRAWN_DT_TM))

df_wide <- df_wide %>%
  anti_join(discordant_AFPs, by=c("EMPI", "ORDER_ID"))

log_text <- 'Cerner and Maciel AFP discordant'
glue('[FILTER] {text}: Rows {n_start}->{n_end} (Diff: {n_diff})',
      text=log_text, n_start = pre_df_sum$N, n_end = nrow(df_wide), n_diff = n_start - n_end)
glue('[FILTER] {text}: Patients {pt_start}->{pt_end} (Diff: {pt_diff})',
      text=log_text, pt_start = pre_df_sum$N_pts, pt_end = n_distinct(df_wide$EMPI), pt_diff = pt_start - pt_end)
glue('[FILTER] {text}: Pts-days {pt_days_start}->{pt_days_end} (Diff: {pt_days_diff})',
        text=log_text, pt_days_start = pre_df_sum$N_pt_days, pt_days_end = n_distinct(df_wide$EMPI, df_wide$DRAWN_DT_TM), pt_days_diff = pt_days_start - pt_days_end)
```

### Input checking
#### Weight
```{r}
df_wide %>%
  ggplot(aes(x=weight)) +
  geom_histogram()
```

#### Exclude weight outliers
```{r}
pre_df_sum <- df_wide %>%
  summarize(N=n(),
            N_pts = n_distinct(EMPI),
            N_orders = n_distinct(ORDER_ID),
            N_pt_days = n_distinct(EMPI, DRAWN_DT_TM))

df_wide <- df_wide %>%
  filter(weight > 50 &
           weight < 800)

log_text <- 'Weight outliers'
glue('[FILTER] {text}: Rows {n_start}->{n_end} (Diff: {n_diff})',
      text=log_text, n_start = pre_df_sum$N, n_end = nrow(df_wide), n_diff = n_start - n_end)
glue('[FILTER] {text}: Patients {pt_start}->{pt_end} (Diff: {pt_diff})',
      text=log_text, pt_start = pre_df_sum$N_pts, pt_end = n_distinct(df_wide$EMPI), pt_diff = pt_start - pt_end)
glue('[FILTER] {text}: Pts-days {pt_days_start}->{pt_days_end} (Diff: {pt_days_diff})',
        text=log_text, pt_days_start = pre_df_sum$N_pt_days, pt_days_end = n_distinct(df_wide$EMPI, df_wide$DRAWN_DT_TM), pt_days_diff = pt_days_start - pt_days_end)
```

#### Number of fetuses
```{r}
df_wide %>% count(`Number of Fetuses.`)
```

#### Exclude number of fetuses not 1 or 2
```{r}
pre_df_sum <- df_wide %>%
  summarize(N=n(),
            N_pts = n_distinct(EMPI),
            N_orders = n_distinct(ORDER_ID),
            N_pt_days = n_distinct(EMPI, DRAWN_DT_TM))

df_wide <- df_wide %>%
  filter(`Number of Fetuses.` %in% 1:2)

log_text <- 'Number of fetuses check'
glue('[FILTER] {text}: Rows {n_start}->{n_end} (Diff: {n_diff})',
      text=log_text, n_start = pre_df_sum$N, n_end = nrow(df_wide), n_diff = n_start - n_end)
glue('[FILTER] {text}: Patients {pt_start}->{pt_end} (Diff: {pt_diff})',
      text=log_text, pt_start = pre_df_sum$N_pts, pt_end = n_distinct(df_wide$EMPI), pt_diff = pt_start - pt_end)
glue('[FILTER] {text}: Pts-days {pt_days_start}->{pt_days_end} (Diff: {pt_days_diff})',
        text=log_text, pt_days_start = pre_df_sum$N_pt_days, pt_days_end = n_distinct(df_wide$EMPI, df_wide$DRAWN_DT_TM), pt_days_diff = pt_days_start - pt_days_end)
```


## Export data
```{r}
file_out_list <- c("..", "data", "msAFP.processed.csv")
file_out_path <- do.call(file.path, as.list(file_out_list))
write_csv(x=df_wide, file=file_out_path)
```


